Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex
touching up abstract

\begin{abstract}
The extended \kep\ mission, \KT, is now providing photometry of new fields every 
three months in a search for transiting planets.
In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet 
candidates orbiting 31 stars in \KT\ \Ci.
In this contribution, we present stellar and planetary properties for all systems.
We combine ground-based seeing-limited survey data and
adaptive optics imaging with an automated transit analysis scheme to validate
\Nvalidated\ candidates as planets
and identify \Nfp\ candidates as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a $2.24 \pm 0.25 R_\odot$ planet with $T_{eq} = 271 \pm 16$ K and an
orbital period of 33 days.
We also present two new open-source software packages that enabled this analysis:  
\texttt{isochrones}, a flexible tool for fitting theoretical stellar 
models to observational data to determine stellar properties; and 
\texttt{vespa}, a new general-purpose implementation
of the \citet{Morton12} procedure to calculate false positive probabilities
and statistically validate transiting exoplanets.
\end{abstract}

>>>>

\begin{abstract}
The extended \kep\ mission, \KT, is now providing photometry of new fields every 
three months in a search for transiting planets.
In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet 
candidates orbiting 31 stars in \KT\ \Ci.
In this contribution, we present stellar and planetary properties for all systems.
We combine ground-based seeing-limited survey data and
adaptive optics imaging with an automated transit analysis scheme to validate
\Nvalidated\ candidates as planets
and identify \Nfp\ candidates as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a $2.24 \pm 0.25 R_\odot$ planet with $T_{eq} = 271 \pm 16$ K and an
orbital period of 33 days.
We also present two new open-source software packages that enabled this analysis:  
\texttt{isochrones}, a flexible tool for fitting theoretical stellar 
models to observational data to determine stellar properties; and 
\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
and statistically validate transiting exoplanets.
\end{abstract}
